
I'm deeply grateful to Professor Serafeim for introducing me into the compelling and innovative world of decarbonization. His contagious enthusiasm for studying analytically the climate transition from a business perspective has been a privilege to learn from. George is an inspiring instructor, and any student would be lucky to have him as a mentor. My gratitude also extends to Professor Rader for caring so much about this thesis and for his passion for applied statistics and modeling real-world problems, bridging theory and practice. I will always be grateful with the dedication with which Kevin jumped into the topic of decarbonization, providing the most important suggestion of using Mixed Effects regression for this analysis. 

I would like to thank all the instructors who went above and beyond to support me in my undergraduate journey at Harvard. Professor Lerner for being an incredible mentor and for sharing his passion for entrepreneurship, Professor Blizstien for his incredible statistics courses, Professor Barak for his introduction to theoretical computer science. Thank you for giving me the opportunity to be a teaching fellow in your courses, I could not be more fortunate to have had these teaching experiences.

My sincere appreciation also goes to Fabrizio Zichichi, Ahmet Atamen, and Paul Bowmar for being incredible professional mentors and for going above and beyond to introduce me to the world of energy commodities. 

Last but not least, a special thanks goes to my high school, Liceo Scientifico S.S. Cannizzaro in Palermo, and to its incredible Professors Giardina, Santomarco, Zanca, and Cimino. Without them, my Harvard journey would not have been possible.


